A systematic search for transiting planets using \KT

### 2015-02-06 ms.tex
More intro

Good photometry relies on either a near-perfect flat-field
and pointing model or data-analysis techniques that are
insensitive to such variations.
The flat-field for \kepler\ was measured on the ground before the launch of 
the spacecraft, but (blah blah it sucks for describing the FF now).
Inference of the flat field is challenging because of the nature of the
spacecraft's observations: point sources are observed with relatively limited
spacecraft motion, and only a few percent of the data are actually stored and
downloaded to Earth.
Therefore, much of the effort in \KT\

In this \paper\ we present an example of the latter---a
data-analysis technique for exoplanet search and characterization that
is insensitive to spacecraft-induced (or, in general,
hardware-induced) trends in the light curves.

...simultaneous fitting of systematics and transit signals is a way of
searching for (and measuring) exoplanet signals independent of the
systematics, provided that the systematics lie in the domain of the
model.

...put in a warning here about \foreign{a priori} ``fit and subtract''
or ``correction'' of light curves.  These methods are very sensitive
to over-fitting in general, so either the investigator must
artificially restrict the model freedom or else do clever
data-censoring methods to avoid it (cite Dun AAS and in prep here).

>>>>

Good photometry relies on either a near-perfect flat-field
and pointing model or data-analysis techniques that are
insensitive to such variations.
The flat-field for \kepler\ was measured on the ground before the launch of 
the spacecraft, but (blah blah it sucks for describing the FF now).
Inference of the flat field is challenging because of the nature of the
spacecraft's observations: point sources are observed with relatively limited
spacecraft motion, and only a few percent of the data are actually stored and
downloaded to Earth.
Therefore, much of the effort in \KT\ is focused on the potential of the latter.

Previous studies have developed methods to work with \KT\ data. 
\citet{vanderburg-a} extract aperture photometry from the pixel data
and decorrelate with image centroid position, producing light curves for each
star that are ``corrected'' for the spacecraft motion. 
These data have produced the first confirmed planet found with 
\KT\ \citep{vanderburg-b}. 
\citet{crossfield} iteratively construct a robust Gaussian Process
model for the photometry as a function of the measured centroids and de-trend
using the mean prediction from that model.

In both of these cases, the authors follow a standard procedure when working 
with \kepler\ data: ``correcting'' the light curve as a step before the search
for transiting planets.
Light curves from the primary \kepler\ mission are typically de-trended to
remove the effects of stellar variability before searching for transiting 
planets. 
With \KT, the authors of each of these papers fit and subtract their measured
effects from the spacecraft pointing variations and stellar variability.
Such a technique can be extremely dangerous.
Small signals, such as planet transits, can be partially absorbed into the 
assumed-stellar signals, making each individual transit event appear 
shallower.
Small planets that should appear just above a specific signal-to-noise
threshold could then be missed because of the de-trending.

The alternative to this approach is to simultaneously fit both the systematics
and the transit signals. 
This method enables us to search for and measure exoplanet signals 
independently of an estimate of the systematics, provided that the systematics
lie in the domain of the model.
The likelihood of the simultaneous fit of the systematics and transit signals
to the data can then be compared to the likelihood of the fit of the systematics
alone, reducing exoplanet ``search'' to a simple model comparison problem.

In this \paper\ we present a
data-analysis technique for exoplanet search and characterization that
is insensitive to spacecraft-induced (or, in general,
hardware-induced) trends in the light curves.

(cite Dun AAS and in prep here).
